Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-10 docs/google-research-awards-latam/main.tex
pass on proposal

JavaScript is one of the most popular programming languages of
today~\cite{business-insider,stackify}. Its niche is front-end and
back-end web development\Comment{, supported several frameworks and
  runtimes (\eg{}, Express.js and Node.js)}, although the languagre
has been used in other contexts.

Recently, the JavaScript specification went through a bigger change
compared to prior releases\footnote{Called by the name of ECMAScript6
  (ES6)~\cite{es6-features}}. This is natural as requests for new
features are common in popular programming languages. Because of
portability~\cite{kangax}, compliance with the new standard is
important for every engine implementation (\eg{}, Google's
V8\Fix{cite}, Mozilla's SpiderMonkey\Fix{cite}, and Microsoft's
Chakra\Fix{cite}).

@@

As in any piece of software, changes in the specification often demand
sensible changes in implementations that could lead to regressions. In
fact, several of these regressions have been reported, some of which
were reported by our team (confirmed by engine developers; see
Section~\ref{sec:results}) using a prototype of our solution (see
Section~\ref{sec:design}).

@@

Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
random-based\Fix{cite}) and whether or not coverage information is
taken into account in the fuzzing process.\Fix{elaborate...}

>>>>

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify}. Its niche is front-end and
back-end web development\Comment{, supported several frameworks and
  runtimes (\eg{}, Express.js and Node.js)}.

Engine implementations (\eg{}, Google's V8\Fix{cite}, Mozilla's
SpiderMonkey\Fix{cite}, and Microsoft's Chakra\Fix{cite}) need to
follow the constant changes in the language
specification~\cite{kangax}. In fact, recently, the JavaScript
specification went through a bigger change compared to prior
releases\footnote{Called by the name of ECMAScript6
  (ES6)~\cite{es6-features}}. As in any piece of software, changes in
the specification often demand sensible changes in implementations
that could lead to errors, including regressions. In fact, bugs in JS
implementations are often reported by the general public, some of
which were reported by our team.

%% (confirmed by engine developers; see
%% Section~\ref{sec:results}) using a prototype of our solution (see
%% Section~\ref{sec:design}).

The lack of executable specifications that could be used as oracles is
an important obstacle for test generation--it prevents detection of
errors which are not explicit, like a crash.  The novelty of our
approach is the use of multiple engine implementations to assess input
validity and output correctness. \emph{Differential testing}\Fix{cite}
has been applied in a variety of contexts\Fix{cite cite}, but it has
not been used to find functional bugs in JS engines.

@@

@@

Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
random-based\Fix{cite}) and whether or not coverage information is
taken into account in the fuzzing process.
